% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Luo Jia}

\basicInfo{
  \email{me@luojia.cc} \textperiodcentered\ 
  \phone{(86) 150-6770-6592} \textperiodcentered\ 
  \github[luojia65]{https://github.com/luojia65}\textperiodcentered\ 
  \homepage{https://luojia.cc}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Huazhong University of Science and Technology (HUST)}, Wuhan, China}{2018/09 -- Present}
\textit{Undergraduate student} in Computer Science (CS), Graduation Date: 2022/06

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Hangzhou EaseCation Information Technology Co.,Ltd.}, Hangzhou, China}{2015/05 -- Present}
\role{Distributed Systems}{Dept. of Game Engine, Manager: Fang Yizhou}
Taken part in building servers to process massive users for a popular mobile phone game.
\begin{itemize}
  \item Developed parts of server-side game engines including Nukkit. Worked together with NetEase Games.
  \item Help creating iTX Nemisys distributing system to handle 20k+ online users with rapid data exchange.
\end{itemize}

\datedsubsection{\textbf{The Funcraft Workgroup (NPO)}, Ningbo, China}{2014/11 -- 2015/05}
\role{Opensource Developer / Database Manager}{Development Team One}
Built open source programs to enrich the ecosystem of game engines.
\begin{itemize}
  \item Help crating the CodeFunCore framework, utils for internal resource distribution and managemant.
  \item Designed database structure and procedures for Funcraft, later used in EaseCation to carry 29m+ users.
\end{itemize}

\section{\faBars\ Projects}
\datedsubsection{\textbf {Nukkit Game Engine}}{https://github.com/nukkit/nukkit}
Popular feature-rich commercial server side game engine with good ecosystem. 700+ stars on GitHub.
\begin{itemize}
  \item Full support for complex game logic and client editions with a developer-friendly plugin system.
  \item Java's popular Netty based network layer, capable to iTX Synapse server grouping protocol.
  \item Online for years; commented "Good" by studio in NetEase; adopted by 24serv, a Russian VPS host.
\end{itemize}

\datedsubsection{\textbf {Coruscant (WIP)}}{https://github.com/luojia65/coruscant}
Experimental game engine library. Contains data serialization, noise generation and file formats by now.
\begin{itemize}
  \item Supports Rust-favored Serde framework, serialize NBT format up to 790 megabytes per second.
  \item Planned to use SIMD instructions to noise generation, UTF-8 validation and performing string unescape. 
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf {Programming Languages:} in favor of Rust. Comfortable with Kotlin/Go/Java/MySQL/C\#/Assembly.
  \item \textbf {Rust: 1 year} of experience. Familiar with Mio/Serde for network, Embedded-Hal for embedded. Learning Vulkano/Actix-Web. Major use in both exercising, learning algorithms and building projects.
  \item \textbf {SIMD:} understand the FastJSON algorithm and simple accelerations, learning SIMD for cryptography. Familiar with x86\_64 sse/avx, both intrinsics and assembly; learning arm neon and RISC-V's V extension.
  \item \textbf {Commercial Projects:} good on them. Experienced in maintaining and improving security system for massive users. Sensitive on common demands and designs for large scale projects.
  \item \textbf {Opensource:} very active on community. Submitted RFC 2517 to the Rust programming language. Active to share exercise projects on GitHub. Publish open source crates on crates.io website.
  \item \textbf {Writing:} published articles on columns, have a good responsibility on translating esp. proper names.
  \item \textbf {Developing Tools:} fluent on VSCode, comfortable with JetBrains IDEs.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{Rust Internals: \textit {New User of the Month Award}; 24 person per year}{2018/08}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item My real name is Jiang Zhouqi; Luo Jia is my penname.
  \item Blog: https://luojia.cc (not frequently updated)
  \item GitHub: https://github.com/luojia65
  \item Zhihu column: https://zhuanlan.zhihu.com/c\_1078248076300521472
  \item Languages: English - Maybe fluent, Mandarin - Native speaker, Russian - Only some from co-working
  \item Play several traditional Chinese instruments
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
